Constructing the transition graphs of interacting hysterons

### 2022-06-02 Paper_draft.tex
Reworked reference to design ineqs to reflect moving section to SI & merged motivation to candidate graphs with corresponding method section; changed title of model section

\section{Setup}

@@

\section{Topological approach}

@@

Instead of evaluating all permutations of the total order of the switching fields, we find it more useful to take a reverse approach by starting from the topology. We first construct a number of candidate graphs, which describe the behaviour of a hysteron system in a well-defined way but are not necessarily realizable. We then generate a set of inequalities that the switching fields must obey so that the given candidate graph is obtained. Finally, we check whether the candidate graph can be realized by checking whether the generated set of inequalities has a solution. We thus obtain a list of possible graphs.\\

@@

\section{Constructing graphs}\label{sec:constructing_graphs}
We here establish a method for finding the transition graphs that are possible for coupled hysterons. We first discuss in section \ref{ssec:candidate_graphs} how one can generate a list of candidate graphs that includes all possible graphs for a given number of hysterons $N$. Next, in section \ref{ssec:realizability}, we explain how to evaluate whether or not a graph is realizable by checking whether its underlying design inequalities have a solution. Finally, we improve on the candidate graph method by introducing the concept of base graphs. 

>>>>

\section{Model}

@@

\section{Constructing possible graphs}

@@

Instead of evaluating all permutations of the total order of the switching fields, we find it more useful to take a reverse approach by starting from the topology. We first construct a number of candidate graphs, which describe the behaviour of a hysteron system in a well-defined way but are not necessarily realizable. We then check whether each graph is realizable by evaluating whether there is a region in the parameter space of switching fields corresponding to the graph.\\
The region in parameter space associated with each graph is bounded by a set of linear inequalities that the switching fields must obey, which we refer to as the design inequalities. We generate the design inequalities systematically by combining the conditions on each individual transition (see SI). If the solution space of a graph's design inequalities is not empty, then the graph is realizable. Thus, one can find the possible graphs for $N$ hysterons by first generating the candidate graphs, then checking whether each graph's design inequalities have a solution.\\

@@

We here establish our method for finding the transition graphs that are possible for coupled hysterons. We first discuss in section \ref{ssec:candidate_graphs} how one can generate a list of candidate graphs that includes all possible graphs for a given number of hysterons $N$. Next, in section \ref{ssec:realizability}, we explain how to evaluate whether or not a graph is realizable by checking whether its underlying design inequalities have a solution. Finally, we improve on the candidate graph method by introducing the concept of base graphs. 
